---
title: "Prediction Assignment Writeup"
author: "Jinkwan Hong"
date: "2019년 1월 10일"
output: html_document
---

---
Prediction for case 1 ~ 20
---

less than 2000 words
less than 5 figures

# Main title?

## Executive Summary

In this work, we are going to answer the question of whether it's possible to use accelerometers data to classify 5 different type of barbell lift. The data was collected from 6 different participants and 4 different accelerometers on each participants. The sensors were attached to belt, forearm, arm, and dumbell. 

data set can be found:  
training data set: https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv  
test data set: https://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv  


## Getting data set

```{r }
### Getting data
### This chunk check the fold and see if the files exist and if only they don't exist download the file from the URL given.

trainURL <- 'https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv'
testURL <- 'https://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv'
dataDir <- './data/'
destTrainFile <- 'pml_training.csv'
destTestFile <- 'pml_testing.csv'
destTrainPath <- paste0(dataDir, destTrainFile)
destTestPath <- paste0(dataDir, destTestFile)

if(!dir.exists(dataDir)){
  dir.create(dataDir)
} 

if(!file.exists(paste(dataDir,destTrainFile))){
  download.file(trainURL, destfile = destTrainPath)
}

if(!file.exists(paste(dataDir,destTestFile))){
  download.file(testURL, destfile = destTestPath)
}

```
```{r}
### data loding
### There are 160 columns in both Training and Testing data set.
### Training data set: 19622 rows, Testing data set: 20 rows
set.seed(42)
trainData <- read.csv(destTrainPath)
cvData <- read.csv(destTestPath)
dim(trainData)
```


```{r echo = FALSE}
### Importing library
library(caret); library(Hmisc); library(ggplot2);library(rpart);library(rpart.plot);library(gbm)
```

## Features

### EDA & Preprocessing

```{r}
plot(trainData$classe)
```
  

We have enough samples of each types of barbell lifts. The data is sorted in alphabetical order by barbell lift types. More data in type A than others but the sampling should not affect data distribution.

```{r}
### Splitting data
inTrain <- createDataPartition(y=trainData$classe, p=0.75, list = FALSE)
training <- trainData[inTrain,]
testing <- trainData[-inTrain,]
```

### Preprocessing

### Feature selection

Dropping nearly zero variance variables

```{r}
NZV <- nearZeroVar(training)
training <- training[,-NZV]
testing <- testing[,-NZV]
```

Dropping 1 ~ 5th columns and columns that are mostly NA

```{r}
training <- training[,-(1:5)]
testing <- testing[,-(1:5)]
mostNA    <- sapply(training, function(x) mean(is.na(x))) > 0.95
training <- training[, mostNA==FALSE]
testing  <- testing[, mostNA==FALSE]
dim(training)
```



## Algorithm

### Random Forest
```{r} 
# Random Forest Model Build
set.seed(301)
controlRF <- trainControl(method="cv", number=3, verboseIter=FALSE)
modRF <- train(classe ~ ., data=training, method="rf",
                          trControl=controlRF)
modRF$finalModel
```

```{r}
# Prediction on Test dataset with Random Forest Model

preditionRF <- predict(modRF, newdata=testing)
confMatRF <- confusionMatrix(preditionRF, testing$classe)
confMatRF
accuracyRF <- confMatRF$overall['Accuracy']
```

Random Forest Accuracy: `r accuracyRF`

### Decision Tree

```{r}
# model fit
set.seed(301)
modDT <- rpart(classe ~ ., data=training, method="class")
#fancyRpartPlot(modDT)
rpart.plot(modDT)

```

```{r}
# prediction on Test dataset
predictDT <- predict(modDT, newdata=testing, type="class")
confMatDT <- confusionMatrix(predictDT, testing$classe)
confMatDT
accuracyDT <- confMatDT$overall['Accuracy']
```
Decision Tree Accuracy: `r accuracyDT`

### Gradient Boosting Machine 

```{r}
# model fit
set.seed(301)
controlGBM <- trainControl(method = "repeatedcv", number = 5, repeats = 1)
modGBM  <- train(classe ~ ., data=training, method = "gbm", trControl = controlGBM, verbose = FALSE)
modGBM$finalModel
```

```{r}
# prediction on Test dataset
predictGBM <- predict(modGBM, newdata=testing)
confMatGBM <- confusionMatrix(predictGBM, testing$classe)
confMatGBM
accuracyGBM <- confMatGBM$overall['Accuracy']
```

Decision Tree Accuracy: `r accuracyGBM`

## Applying the most accurate model to the Test Data

Within this prediction Random Forest has shown the most accurate. Random Forest model will be applied to the 20 quiz data.


```{r}
predictCV <- predict(modRF, newdata = cvData)
predictCV
```